### 2014-04-13 pot/LaTeX/Schlather.tex
updated manuscript
Added in include command for the conditional distribution for u | y

\subsection{Complete data}\label{s:model}
Consider the spatial process
\begin{align} \label{fullmodel}
  Y_t(\bs) &= X_t(\bs) \beta + e_t(\bs)\\
  e_t(\bs) &= \sigma \delta | u_t(\bs) | + v_t(\bs)
\end{align}
where $u_t(\bs) = u_{tl}$ if $s \in P_{tl}$ where $P_{t1}, \ldots, P_{tL}$ form a partition, and $u_{tl} \iid N(0, 1)$, $\delta \in (-1, 1)$ controls skew, and $v_t(\bs)$ is a spatial process with mean zero and variance $\sigma^2(1 - \delta^2)$.
Then $Y_t(\bs)$ is skew normal within each partition \citep{Minozzo2012}.
We model this with a Bayesian hierarchical model as follows.
Let $w_{t1}, \ldots, w_{tL}$ be partition centers so that $P_{tl}$ includes all spatial locations $\bs$ that are within the partition.
Then
\begin{align} \label{eq:hier}
    Y_t(\bs) \mid \Theta &= \mu_t(\bs) + v_t(\bs) \\
    \mu_t(\bs) &= X_t(\bs) \beta + \sigma \delta | u_{tl} |
\end{align}
where $l = \argmin_j ||\bs - w_j ||$ and $\Theta = \{ u_{t1}, \ldots, u_{tL}, w_{t1}, \ldots, w_{tL}, \beta, \rho, \nu, \sigma \}$ are the random effects, knot locations, and parameters for the mean, and spatial covariance.

@@

\subsection{Parameter updates}\label{s:params}
To update $\Theta$ given the current value of the complete data $\bY_1, \ldots, \bY_T$, we use a standard Metropolis update.

@@

\section*{Appendix A.1: MCMC Details}

\subsection*{Priors}
For a given day
\beqn
	r_{j} &\iid& \mbox{IG}(\xi_r, \sigma_r)\nonumber\\ 
	\sigma_r &\sim& \mbox{Gamma}(0.1, 0.1)\nonumber\\
	\xi_r &\sim& \mbox{Discrete Uniform}(0.5, 30)\nonumber\\
	\bv_{j} &\iid& \mbox{Uniform}(\calD)\nonumber\\
	\mu(\bs) &\sim& \mbox{MVN}(0, \mbox{diag}(10))\nonumber\\
	\log(\rho) &\sim& \mbox{N}(0, 10)\nonumber\\
	\log(\nu) &\sim& \mbox{N}(-1, 1)\nonumber\\
	\alpha &\sim& \mbox{Unif}(0, 1)\nonumber
\eeqn
where $v_j$ are the locations of the spatial knots over $\calD$, $\alpha$ is a parameter controlling the proportion of $r^2_{j}$ that is attributed to the nugget and partial sill. 
If $\alpha = 0$, then $r^2_{j}$ can be entirely attributed to the nugget effect, and if $\alpha = 1$, then $r^2_{tj}$ can be entirely attributed to the partial sill.
We use Gibbs sampling for $r_j, \sigma_r$, and $\mu(\bs)$. 
All other parameters are sampled using a random-walk Metropolis Hastings algorithm.

>>>>

\subsection{Complete data}\label{s:model}
Consider the spatial process
\begin{align} \label{eq:fullmodel}
  Y_t(\bs) &= X_t(\bs) \beta + e_t(\bs)\\
  e_t(\bs) &= \sigma \delta | u_t(\bs) | + v_t(\bs)
\end{align}
where $u_t(\bs) = u_{tl}$ if $s \in P_{tl}$ where $P_{t1}, \ldots, P_{tL}$ form a partition, and $u_{tl} \iid N(0, 1)$, $\delta \in (-1, 1)$ controls skew, and $v_t(\bs)$ is a spatial process with mean zero and variance $\sigma^2(1 - \delta^2)$.
Then $Y_t(\bs)$ is skew normal within each partition \citep{Minozzo2012}.
We model this with a Bayesian hierarchical model as follows.
Let $w_{t1}, \ldots, w_{tL}$ be partition centers so that $P_{tl}$ includes all spatial locations $\bs$ that are within the partition.
Then
\begin{align} \label{eq:hier}
    Y_t(\bs) \mid \Theta &= \mu_t(\bs) + v_t(\bs) \\
    \mu_t(\bs) &= X_t(\bs) \beta + \sigma \delta | u_{tl} |
\end{align}
where $l = \argmin_j ||\bs - w_j ||$ and $\Theta = \{ u_{t1}, \ldots, u_{tL}, w_{t1}, \ldots, w_{tL}, \beta, \rho, \nu, \sigma \}$ are the random effects, knot locations, and parameters for the mean, and spatial covariance.

@@

\subsection{Parameter updates}\label{s:params}
To update $\Theta$ given the current value of the complete data $\bY_1, \ldots, \bY_T$, we use a standard Gibbs updates for all parameters except for the knot locations which are done using a Metropolis update.
See Appendix A.1 for details regarding Gibbs sampling and $|u_t(\bs)|$.

@@

\section*{Appendix A.1: Half-Normal results}
\input{halfnormal.tex}

\section*{Appendix A.2: MCMC Details}

\subsection*{Priors}
